The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)

### 2018-12-14 outputs/docs/events/paper.Rmd
Update graphs in appendix fo counts

The main data source for our paper is the text record, known as 'Hansard', of what was said in the Australian Federal Parliament. From this we create a dataset based on the sitting days from 1901 through to 2018. We have records for 7,934 days in the 'House of Representatives' (lower house) and 6,746 days in the 'Senate' (upper house). In contrast to the US, but similar to Canada and the UK, the executive is drawn from the legislature, and the Australian prime minister typically sits in the lower house. Unlike Canada or the UK, both houses are elected, although each has different mechanisms and constituencies. Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case; remove names, numbers, and punctuation; join commonly co-located words; and remove stop words.

@@

The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)). This is evidence to suggest that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time. We use Hansard records on a daily basis in this paper. We pre-process our text before applying a topic model. The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales. We do not stem the words because @SchofieldMimno2016 suggest that there may not be any significant benefit. Then the sentences are de-constructed and each word considered individually. The resulting dataset used for analysis contains counts of words by day for each of the 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]

@@

Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM. We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 822 **[UPDATE]** sitting periods over the period 1901 to 2018 inclusive. Appendix \@ref(wastonywrong) contains more information about the sitting patterns over time.

@@

Using text as data allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify associations and patterns that may otherwise be overlooked. That said, text analysis has well-known shortcomings and weaknesses and should be considered a complement to more detailed analysis such as qualitative methods and case studies. For instance, the use of topic models is problematic because of the need to interpret the topics. This can be difficult especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed. Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning. For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics. Even after doing this there tend to be topics that are not overly meaningful, especially on their own. One way to get around using topic models is to use the words more directly, for instance word2vec and other approaches. As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could explore that direction.

@@

@@

@@

<!-- The first step is to scrape the websites for the PDFs. -->

<!-- ```{r scrapingexample, echo=TRUE, eval = FALSE} -->
<!-- visit_address_and_save_PDF <- -->
<!--   function(name_of_address_to_visit, -->
<!--            name_of_where_to_save) { -->
<!--     # Do the actual downloading of the PDF -->
<!--     download.file(name_of_address_to_visit, name_of_where_to_save) -->
<!--     # Helpful so that you know progress when running it on all the records -->
<!--     print(paste("Done with", name_of_where_to_save, "at", Sys.time()))   -->
<!--     # Space out your requests so you don't overwhelm the website -->
<!--     Sys.sleep(sample(15:30, 1))  -->
<!--   } -->
<!-- ``` -->

@@

# Sitting periods over time {#wastonywrong}

**[Add the graph.]**

>>>>

The main data source for our paper is the text record, known as 'Hansard', of what was said in the Australian Federal Parliament. From this we create a dataset based on the sitting days from 1901 through to 2018. We have records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house). In contrast to the US, but similar to Canada and the UK, the executive is drawn from the legislature, and the Australian prime minister typically sits in the lower house. Unlike Canada or the UK, both houses are elected, although each has different mechanisms and constituencies. Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case; remove names, numbers, and punctuation; join commonly co-located words; and remove stop words.

@@

The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)). This is evidence to suggest that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time. We use Hansard records on a daily basis in this paper. We pre-process our text before applying a topic model. The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales. We do not stem the words because @SchofieldMimno2016 suggest that there may not be any significant benefit. Then the sentences are de-constructed and each word considered individually. The resulting dataset used for analysis contains counts of words by day for 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]

@@

Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM. We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 822 **[UPDATE]** sitting periods over the period 1901 to 2018 inclusive. Appendix \@ref(hansardsummarystatistics) contains more information about the sitting patterns over the course of the year, which have changed considerably since Federation.

@@

Using text as data allows us to conduct larger-scale analysis that would not be viable using less-automated approaches and so researchers may be able to identify associations and patterns that would otherwise have been overlooked. That said, the approach has well-known shortcomings and weaknesses, such as those documented by @GrimmerStewart2013. Our paper should thus be considered a complement to more detailed analysis such as qualitative methods and case studies. An example of one of the more glaring issues when using topic models is the need to interpret the topics. This can be difficult, especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed. Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning. Most obviously the number of topics needs to be specified, but there are also more nuanced aspects to be aware of. For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics. Even after doing this there tend to be topics that are not overly meaningful, especially on their own. One way to get around using topic models is to use a supervised learning approach, such as that used by @AshMorelliOsnabru2018 in the context of New Zealand Hansard. Another is to use the words more directly, for instance word2vec and other approaches. As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could explore that direction.

@@

### Counts per year

@@

### Distribution over the year

The distribution of sitting days over the course of the year changes over time. It was initially more piecemeal. This can be seen by comparing the pattern of sitting days in the years to 1920 (Figure \@ref(fig:dayssattonineteentwenty)) with those in the 19 years from, and including, 2000 (Figure \@ref(fig:dayssatfromtwothousand)).

```{r dayssattonineteentwenty, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
knitr::include_graphics("../../figures/sitting_dates_before_1920.pdf")
```

```{r dayssatfromtwothousand, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
knitr::include_graphics("../../figures/sitting_dates_from_2000.pdf")
```

The largest gap between sitting dates for both the House of Representatives and the Senate is 284 days, which happened when neither house sat between 25 November 1910 and 5 September 1911. The next longest gap is 244 the House of Representatives and 243 for the Senate when the lower house last sat on 9 October 1924, the upper house last sat on 10 October 1924 and neither sat again until 10 June 1925.

@@

The first step is to scrape the websites for the PDFs.

```{r scrapingexample, echo=TRUE, eval = FALSE}
name_of_address_to_visit <- c("wwww1", "wwww2")
name_of_where_to_save <- c("2017-02-01.pdf", "2017-02-02.pdf")

visit_address_and_save_PDF <-
  function(name_of_address_to_visit,
           name_of_where_to_save) {
    # Do the actual downloading of the PDF
    download.file(name_of_address_to_visit, name_of_where_to_save)
    # Helpful so that you know progress when running it on all the records
    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))
    # Space out your requests so you don't overwhelm the website
    Sys.sleep(sample(15:30, 1))
  }
```

@@
